Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-01-25 article/Article.tex
refonte biblio, MAJ des affiliations, et ajout de figures

@@

@@

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$} {\small{and}} David Legland{$^2$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et Reproduction, Jouy en Josas, F-78350, France.\\
{$^2$}INRA, UMR 0782, G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France.}

@@

Dans l'intro, mettre :
* mesure perimetre ou surface est important
* liste des differentes methodes pour mesures surface / perimetre
    * choix marching cubes pour comparer
* parler des facteurs de forme et introduire "roundness"
* plan de l'article

@@

% Crofton formula
Perimeter measure of 2D objects, surface area measure of 3D objects 
and more generally $(d-1)$-surface measure of $d$-dimensional objects 
can be expressed in a unified formalism by using the Crofton formula.
This formula consists in integrating the intercept number of the object with
lines of various orientation and positions. Its expression in
the general form is:
\begin{eqnarray}
S^{(d-1)}(X) & = & \frac{d v_d}{\pi}\int_{\mathcal{L}^d}\chi\left(X\cap L\right) dL
\end{eqnarray}
where $X$ is the structure of interest, $v_d$ is the volume of the $d$-dimensional ball,
$\mathcal{L}^d$ is the set of all lines in the $d$-dimensional space. 
The above integral is normalised such that the mass of lines hitting the unit ball 
equals $v_{d-1}$, the measure of the unit ball projection on a $(d-1)$-dimensional plane.

@@

The Crofton formula can be easily applied to discrete binary images \cite{Lang2001, Legland2007}. 
The integral over lines can be decomposed into an integral over a finite set of directions
and an integral over lines parallel to a given direction.
The number of connected components in the intersections of the structure with a discrete line
is obtained by counting the number of intercepts with its boundary.

[Ajouter une formule avec des sommes a la place des integrales]

[dire comment on calcule les poids (1) des espaces entre les droites et (2) des poids associes aux directions]
[Cas des directions principales ($d$ en $nd$) et de toutes les directions (4 en 2D et 13 en 3D)]

@@

% Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=5cm]{images/discreteDisk}
\end{center}
\caption{Discretization of a disk}
\label{fig:DiskDiscretization}
\end{figure}
This paper assumes isotropic resolution, i.e. $\Delta_{i}$ being the same for all $i$.

@@

Perimeter of 2D discretized shapes was measured using Crofton method using 2 and 4 directions, 
and by computing the length of the reconstructed contour (method ?).
Surface area of 3D discretized shapes was measured using Crofton method using 3 and 13 directions, 
and by computing the surface area of the reconstruced shape obtained by the marching cubes algorithm.
The average and the standard deviation of measurements were computed for all shapes discretized
with the same resolution. Effect of orientation was investigated by computing average and standard 
deviation of shapes having the same orientation.

@@

\subsection{Global accuracy}

[Tableaux qui donnent les valeurs moyennes pour les differentes formes]

%
\begin{table}[!htb]
\begin{center}
\begin{tabular}{|c|c|c|c|} \hline 
shape		    & $U$		& $U_d^2$ & $U_d^4$		\tabularnewline \hline
disk		    & $251.33$	& $251.31$ 	& $251.32$ 	\tabularnewline
ring		    & $376.99$	& $376.99$ 	& $377.02$	\tabularnewline
rectangle  $0$ 	& $120.00$ 	&\ \ $94.24$& $112.66$	\tabularnewline
rectangle $30$  & $-$ 		& $127.23$	& $120.82$	\tabularnewline
rectangle $45$  & $-$ 		& $131.95$	& $113.18$	\tabularnewline
\hline
\end{tabular}\end{center}
\caption{\label{tab:Validate-Perimeter}
Differences between theoretical and measured perimeter of planar shapes.
Approximations were computed using $2$ and $4$ directions.
}
\end{table}

\subsection{Position effect}

[On regarde effet de la resolution et de la dispersion des mesures]
[-> 1 graphe 2D, 1 graphe 3D, avec superposition des mesures ?]

\subsection{Orientation effect}

@@

ICOPAN

>>>>

\usepackage{color}

@@

 \definecolor{lightgray}{gray}{.75}
\newcommand{\commentaire}[1]{
\colorbox{lightgray}{#1}
}

@@

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann$^{1,2}$ {\small{and}} David Legland$^{3,4,5}$}

\authoraddress{\small{
{$^1$}INRA, UMR 1198 Biologie du D\'eveloppement et Reproduction, Jouy-en-Josas, F-78350, France\\
{$^2$}ENVA, UMR 1198 Biologie du D\'eveloppement et Reproduction, Jouy-en-Josas, F-78350, France\\
{$^3$}INRA, UMR 0782 G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France\\
{$^4$}AgroParisTech, UMR 0782 G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France\\
{$^5$}INRA, UMR 1318 Institut Jean-Pierre Bourgin, Versailles, F-78026, France
}}

@@

Surface area and perimeter are widely used parameters describing the size of objects observed in images, 
and are commonly used for computing various shape factors.
Unlike the area that can be easily measured by counting pixels belonging to the object, measuring the 
perimeter is not as straightforward, 
and naive methods can lead to huge systematic errors \cite{Klette2004, Legland2007}.
Usually, the countour of the object is extracted, then its length is measured.
The same approach is usually applied to 3D images: the boundary of the 3D object is first reconstructed,
e.g. by using marching cubes \cite{Lorensen1987}, then its surface area is computed by summing 
area of individual triangles.

The Crofton method is an alternative method that allows measuring the perimeter of 2D objects,
the surface area of 3D objects, and more generally the $(d-1)$-dimensional measure of $d$-dimensional 
object boundary. 
\commentaire{Ajouter un petit argumentaire sur convergence des mesures avec Crofton.}

The article first recalls the mathematical principles of $d$-perimeter measures in digital images
using the Crofton method. An efficient implementation based on run-length encoding is then presented.
The method is evaluated on various $2D$ and $3D$ synthetic shapes and compared with other methods.
The effect on the roundness shape factor is also investigated.

@@

% Crofton formula
Perimeter measure of 2D objects, surface area measure of 3D objects 
and more generally $(d-1)$-surface measure of $d$-dimensional objects 
can be expressed in a unified formalism by using the Crofton formula.
This formula consists in integrating the intercept number of the object with
lines of various orientation and positions. Its expression in
the general form is:
\begin{eqnarray}
S^{(d-1)}(X) & = & \frac{d \cdot v_d}{\pi}\int_{\mathcal{L}^d}\chi\left(X\cap L\right) dL
\end{eqnarray}
where $X$ is the structure of interest, $v_d$ is the volume of the $d$-dimensional ball,
$\mathcal{L}^d$ is the set of all lines in the $d$-dimensional space. 
The above integral is normalised such that the mass of lines hitting the unit ball 
equals $v_{d-1}$, the measure of the unit ball projection on a $(d-1)$-dimensional plane.

@@

The Crofton formula can be easily applied to discrete binary images \cite{Lang2001, Legland2007}. 
The integral over lines can be decomposed into an integral over a finite set of directions
and an integral over lines parallel to a given direction.
The number of connected components in the intersections of the structure with a discrete line
is obtained by counting the number of intercepts with its boundary.
\commentaire{ 
Ajouter une formule avec des sommes a la place des integrales (David)}

\commentaire{dire comment on calcule les poids (1) des espaces entre les droites et (2) des poids associes aux directions}

\commentaire{Cas des directions principales ($d$ en $nd$) et de toutes les directions (4 en 2D et 13 en 3D)}

@@

% Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=5cm]{images/discreteDisk}
\end{center}
\caption{Discretization of a disk}
\label{fig:DiskDiscretization}
\end{figure}

@@

Perimeter of 2D discretized shapes was measured using Crofton method using 2 and 4 directions, 
and by computing the length of the reconstructed contour (Matlab Software was used).
Surface area of 3D discretized shapes was measured using Crofton method using 3 and 13 directions, 
and by computing the surface area of the reconstruced shape obtained by the marching cubes algorithm.
The average and the standard deviation of measurements were computed for all shapes discretized
with the same resolution. Effect of orientation was investigated by computing average and standard 
deviation of shapes having the same orientation.

@@

\subsection{Perimeter of disks at various resolutions}

Figure \ref{fig:MeasureDiskPerimeter} shows average and standard deviation of perimeter
measured on disks with various resolutions. Perimeter measured using Crofton method converges
towards the real value when the resolution increase. 
The convergence speed is faster when four directions are used instead of two, 
and the variability is lower.

% Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=10cm]{images/perimeterDisks}
\end{center}
\caption{Perimeter measure of disks with various resolutions and at random positions}
\label{fig:MeasureDiskPerimeter}
\end{figure}

Perimeters measured with Matlab show similar variability, but the measured values do not
converge toward the true value. This shows the inaccuracy of the method consisting in
counting boundary pixels.

The oscillations of the variability is due to the fact that for disks with diameters equal to an
integer, the number of intersections with horizontal or vertical lines is always the same, 
thus greatly reducing the variability of measures.

\subsection{Perimeter of squares with various orientations}

Figure \ref{fig:MeasureSquareOriented} shows measures obtained on discretized squares (side 30 pixels)
with various orientations. All methods oscillate around the expected value. 
Using Crofton method with only 2 directions can produce greater errors on the measure than with 4 
directions.

% Example of reconstruction of a discrete squares with various orientations
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=8cm]{images/errorSquareRotated}
\includegraphics[width=8cm]{images/errorRelSquareRotated}
\end{center}
\caption{Variations of perimeter measure of a digitized square depending on the orientation}
\label{fig:MeasureSquareOriented}
\end{figure}

@@

\subsection{ICOPAN}

Methods were applied on images acquired within the ICOPAN project \cite{Andrey2010}.
